---
title: "CaseStudy1AKannan"
author: "Adarsh Kannan"
date: "March 23, 2017"
output: html_document
---


## Case Study 1

##Introduction

This case study shows the correlation between countries based on GDP and Education. 

##This chunk code downloads the GDP and Education Files and sets column names

```{r CaseStudy1}
##Downloading GDP

if (!file.exists("data")){
  dir.create("data")
}
fileURL <- "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FGDP.csv"
download.file(fileURL,destfile="C:/Users/user/Desktop/gdp.csv", method='curl')
gdp <- read.csv("C:/Users/user/Desktop/gdp.csv",skip=5,header=FALSE,nrows=200)

##Column Names
colnames(gdp)[1]="CountryCode"
colnames(gdp)[5]="gdp"
gdp$gdp <- as.numeric(gsub(",","",gdp$gdp))

##Download Education File
fileURL <- "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FEDSTATS_Country.csv"
download.file(fileURL,destfile="C:/Users/user/Desktop/gdp.csv", method='curl')
education <- read.csv("C:/Users/user/Desktop/Education.csv",header=TRUE)
```

This Chunk Code sorts, merges, and divides by quantiles
```{r}
##Merge/Sort/Quantile Data
FullData <- merge(gdp,education,by="CountryCode")
FullDataSorted <- FullData[order(FullData$gdp,na.last=NA),]
FullData$quantile <- cut(FullDataSorted$V2,5)
FullDataFinalTable <- table(FullDataSorted$quantile,FullDataSorted$Income.Group)
```

## This is a plot of the GDP value. The plot shows that there is a direct correlation between income group and GDP despite a few outliers. 
```{r GDP Plot, echo=FALSE}
ggplot2<-plot(gdp)
```

Answers
1. 224 IDs match
2. There are two countries that tie for 13th - Granada and St. Kitts
3. High Income OECD Average: 157
   High Income Non-OECD Average: 98
4. 
Summary Statistics:
      High Income OECD  High Income Non-OECD  Low Income  Lower Middle Income Upper Middle Income
Min       13579               2584            596           40                228             
Max       16244600            711050          504431        8221703           2252664
Median    486528.5            28373           8630.5        24272             42945
Mean      1483917.133         104349.8261     27306.05263   256663.5          231847.8
Q1         211146.7            12838           3910.25       2548.75          9613
Q3         1480047.25          131204          18523.25      81448            205789

5.There are 5 countries that are in the lower middle income group but amongst the highest gdp.
                                
                                
                             
                                 
                                 




